---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk[["set"]](
    collapse = TRUE,
    comment = "#>",
    fig.path = file.path("man", "figures", "README-"),
    out.width = "100%"
)
```

# {IssueTrackeR} <a href="https://tanguybarthelemy.github.io/IssueTrackeR/"><img src="man/figures/logo.svg" align="right" height="150" style="float:right; height:150px;"/></a> 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/IssueTrackeR)](https://CRAN.R-project.org/package=IssueTrackeR)
[![R-CMD-check](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/R-CMD-check.yaml)
[![GH Pages built](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/pkgdown.yaml)

[![lint](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/lint.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/lint.yaml)
[![Coverage](https://codecov.io/gh/TanguyBarthelemy/IssueTrackeR/graph/badge.svg)](https://app.codecov.io/gh/TanguyBarthelemy/IssueTrackeR)
[![CodeFactor](https://www.codefactor.io/repository/github/tanguybarthelemy/issuetracker/badge)](https://www.codefactor.io/repository/github/tanguybarthelemy/issuetracker)
<!-- badges: end -->

**{IssueTrackeR}** is an R package designed to retrieve and manage GitHub issues directly within R. This package allows users to efficiently track and handle issues from their GitHub repositories.

This package relies a lot on the package [{gh}](https://github.com/r-lib/gh) to use the GitHub API and retrieve data from GitHub.


## Installation

You can install the development version of {IssueTrackeR} from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("TanguyBarthelemy/IssueTrackeR")
```


## Features

- **Retrieve Issues**: Fetch issues from any (with sufficient rights) GitHub repository.
- **Issue Management**: Class S3 to manage the issues as a datasets within R.
- **Filtering**: Filter issues by labels, content and milestones.


## Usage

```{r, eval = TRUE, echo = TRUE}
library("IssueTrackeR")
```

### Retrieve information from GitHub

To get information from a repository, you can call the functions `get_issues`, `get_labels` and `get_milestones`

```{r, eval = TRUE, echo = TRUE}
# From online
my_issues <- get_issues(source = "online", owner = "jdemetra", repo = "jdplus-main", verbose = FALSE)
my_labels <- get_labels(source = "online", owner = "jdemetra", repo = "jdplus-main")
my_milestones <- get_milestones(source = "online", owner = "jdemetra", repo = "jdplus-main")
```

### Save issues in local

You can also write the datasets in local with `write_issues_to_dataset()`, `write_labels_to_dataset()` and `write_milestones_to_dataset()`:

```{r, eval = TRUE, echo = TRUE}
write_issues_to_dataset(
    issues = my_issues, 
    dataset_dir = tempdir()
)

write_labels_to_dataset(
    labels = my_labels, 
    dataset_dir = tempdir()
)

write_milestones_to_dataset(
    milestones = my_milestones, 
    dataset_dir = tempdir()
)
```

### Options

It is also possible to set option for a R session:

```{r, eval = TRUE, echo = TRUE}
# The directory containing the yaml files in local
options(IssueTrackeR.dataset.dir = tempdir())
# The default GitHub owner
options(IssueTrackeR.owner = "jdemetra")
# the default GitHub repository
options(IssueTrackeR.repo = "jdplus-main")
```

### Retrieve issues from local

Then it's possible to read Issues from local yaml files:

```{r, eval = FALSE, echo = TRUE}
# From local
my_issues <- get_issues(source = "local")
my_labels <- get_labels(source = "local")
my_milestones <- get_milestones(source = "local")
```

### Update full database

You can update your full database of issues, labels and milestones with `update_database()`:

```{r, eval = TRUE, echo = TRUE}
# From online
update_database(verbose = FALSE)
```

## Contributing

Contributions are welcome! Please feel free to submit a pull request or report any issues.

## License

This project is licensed under the MIT License. See the [LICENSE](LICENSE) file for details.
