---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r parameters, include = FALSE}
knitr::opts_chunk[["set"]](
    collapse = TRUE,
    comment = "#>",
    fig.path = file.path("man", "figures", "README-"),
    out.width = "100%"
)
```

# {IssueTrackeR} <a href="https://tanguybarthelemy.github.io/IssueTrackeR/"><img src="man/figures/logo.svg" align="right" height="150" style="float:right; height:150px;"/></a> 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/IssueTrackeR)](https://CRAN.R-project.org/package=IssueTrackeR)
[![R-CMD-check](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/R-CMD-check.yaml)
[![GH Pages built](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/pkgdown.yaml)

[![lint](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/lint.yaml/badge.svg)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/lint.yaml)
[![Coverage](https://codecov.io/gh/TanguyBarthelemy/IssueTrackeR/graph/badge.svg)](https://app.codecov.io/gh/TanguyBarthelemy/IssueTrackeR)
[![muttest](https://img.shields.io/endpoint?url=https://raw.githubusercontent.com/TanguyBarthelemy/IssueTrackeR/badges/.badges/muttest.json)](https://github.com/TanguyBarthelemy/IssueTrackeR/actions/workflows/test-mutation.yaml)
[![CodeFactor](https://www.codefactor.io/repository/github/tanguybarthelemy/issuetracker/badge)](https://www.codefactor.io/repository/github/tanguybarthelemy/issuetracker)
<!-- badges: end -->

**{IssueTrackeR}** is an R package designed to retrieve and manage GitHub issues directly within R. This package allows users to efficiently track and handle issues from their GitHub repositories.

This package relies a lot on the package [{gh}](https://github.com/r-lib/gh) to use the GitHub API and retrieve data from GitHub.


## Installation

You can install {IssueTrackeR} from [CRAN](https://CRAN.R-project.org/package=IssueTrackeR):

```{r install-from-cran, eval = FALSE, echo = TRUE, results = "hide", message = FALSE}
install.packages("IssueTrackeR")
```

### Development

You can install the development version of {IssueTrackeR} from [GitHub](https://github.com/):

```{r install-from-gh, eval = FALSE, echo = TRUE, results = "hide", message = FALSE}
# install.packages("pak")
pak::pak("TanguyBarthelemy/IssueTrackeR")
```

## Features

- **Multi-source support**: Fetch issues from GitHub, GitLab, or local YAML files.
- **Visualization**: Plot issue trends, resolution times, and backlog evolution.
- **Save issues locally**: Write the issues, labels and milestones locally to access it without connection.


## Usage

```{r loading, eval = TRUE, echo = TRUE}
library("IssueTrackeR")
```


### Create a selector

```{r selector, eval = TRUE, echo = TRUE}
# Configure {gitlabr} to retrieve issues from GitLab
gitlabr::set_gitlab_connection(
    gitlab_url = "https://gitlab.com",
    private_token = Sys.getenv("GITLAB_TRACTORTOM_API")
)

# Select repos from GitHub
selector1 <- init_selector(
    source = "GitHub",
    owner = "TanguyBarthelemy",
    repo = "IssueTrackeR"
)

# Select project from GitLab
selector2 <- init_selector(
    source = "GitLab",
    project_id = c(51699988, 29346974, 15028532)
)

# Select list of issues from local files
selector3 <- init_selector(
    source = "local",
    file = file.path(
        system.file("data_issues", package = "IssueTrackeR"),
        "list_issues.yaml"
    )
)

selector_issues <- merge_selector(selector1, selector2, selector3)
selector_other <- merge_selector(selector1, selector2)
```


### Get the issues

To get information from a repository, you can call the functions `get_issues`, `get_labels` and `get_milestones`:

```{r get, eval = TRUE, echo = TRUE}
my_issues <- get_issues(selector = selector_issues)
my_labels <- get_labels(selector = selector_other)
my_milestones <- get_milestones(selector = selector_other)
```


### Save issues in local

You can also write the datasets in local with `write_to_dataset()`:

```{r write, eval = TRUE, echo = TRUE}
write_to_dataset(
    x = my_issues,
    dataset_dir = tempdir()
)

write_to_dataset(
    x = my_labels,
    dataset_dir = tempdir()
)

write_to_dataset(
    x = my_milestones,
    dataset_dir = tempdir()
)
```


### Filtering

You can filter the output based on its content using the `with_text()` function:

```{r filter, eval = TRUE, echo = TRUE}
filtered_issues <- my_issues |> 
    with_labels("bug") |> 
    with_text("format") |>
    with_comments()
```


### Visualisation 


```{r plot, eval = TRUE, echo = TRUE, fig.width = 10, fig.height = 7}
# Plot creation/closure rates
plot(my_issues, type = "created-closed")

# Plot resolution time distribution
plot(my_issues, type = "resolution-time")

# Plot by category (e.g., by creator, milestone, or repo)
plot(my_issues, type = "area-chart", by = "creator", n = 5)
```


## Contributing

Contributions are welcome! Please feel free to submit a pull request or report any issues.

## License

This project is licensed under the MIT License. See the [LICENSE](LICENSE) file for details.
