---
title: "The role of selector in {IssueTrackeR}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The role of selector in {IssueTrackeR}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup-knitr-vignette, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

```{r setup-IssueTrackeR, eval = TRUE, echo = FALSE}
# Handle credentials for GitLab if available
if (Sys.getenv("GITLAB_TRACTORTOM_API") != "") {
    gitlabr::set_gitlab_connection(
        gitlab_url = "https://gitlab.com",
        private_token = Sys.getenv("GITLAB_TRACTORTOM_API")
    )
}
```

# Introduction

In {IssueTrackeR}, a **selector** is a fundamental object used to specify the data sources from which you want to retrieve information (issues, labels, milestones, etc.).

```{r loading-IssueTrackeR}
library("IssueTrackeR")
```

## What is a selector?

A selector is an object of class `SelectorTB`. Technically, it is a list of configurations, where each configuration describes a specific source and the parameters needed to access it.

## Supported sources

A selector can contain different types of sources:

1.  **GitHub**: Uses `owner` and `repo` (or just `owner` to fetch all repositories).
2.  **GitLab**: Uses `project_id`.
3.  **Local**: Uses a path to a `YAML` file containing issue data.
    
**Note**: When using `source = "local"`, functions `get_issues()`, `get_labels()` and `get_milestones()` and `update_database()` will use the `dataset_dir` argument to look for files following the pattern `list_issues_<dataset_name>.yaml`, `list_labels_<dataset_name>.yaml`, or `list_milestones_<dataset_name>.yaml`.

```{r different-sources, eval = TRUE, echo = FALSE}
gh_sel <- init_selector(
    source = "GitHub",
    owner = "TanguyBarthelemy",
    repo = "IssueTrackeR"
)

# GitLab selector
gl_sel <- init_selector(source = "GitLab", project_id = 4578L)

# Local selector
local_sel <- init_selector(
    source = "local",
    dataset_dir = system.file("data_issues", package = "IssueTrackeR"), 
    dataset_name = NULL
)

# Inspecting them
print(gh_sel)
print(gl_sel)
print(local_sel)
```

## How to create a selector?

The main way to create a selector is using the `init_selector()` function.

```{r create_selector}
# Creating a simple GitHub selector
my_sel <- init_selector(
    source = "GitHub",
    owner = "TanguyBarthelemy",
    repo = "IssueTrackeR"
)
```

## How is it displayed?

When you `print()` a `SelectorTB` object, it provides a formatted summary showing the number of selectors and the details for each one.

```{r display_selector}
print(my_sel)
```

## Manipulating a list of selectors

Since a `SelectorTB` is a list, you can combine, extract, or remove selectors.

### Adding a new selector to a list

Use `merge_selector()` to combine multiple selectors into one.

```{r add_selector}
sel1 <- init_selector(
    source = "GitHub",
    owner = "TanguyBarthelemy",
    repo = "IssueTrackeR"
)
sel2 <- init_selector(
    source = "local",
    file = system.file(
        "data_issues", "list_issues.yaml", package = "IssueTrackeR"
    )
)

combined_sel <- merge_selector(sel1, sel2)
print(combined_sel)
```

### Extracting a selector from a list

Use `extract_nth()` to retrieve a specific selector by its index.

```{r extract_selector}
extracted <- extract_nth(combined_sel, 1L)
print(extracted)
```

### Removing a selector from a list

Use `remove_nth()` to remove a selector at a specific position.

```{r remove_selector}
# Let's create a list of 3 selectors to demonstrate
sel3 <- init_selector(
    source = "GitHub",
    owner = "TanguyBarthelemy",
    repo = "IssueTrackeR"
)
list_sel <- merge_selector(sel1, sel2, sel3)

# Remove the second one
reduced_sel <- remove_nth(list_sel, 2L)
print(reduced_sel)
```

## The `IssueTrackeR.selector` option

The package provides a global option `IssueTrackeR.selector`. This option defines the **default selector** used by retrieval functions (like `get_issues()`, `get_labels()`, etc.) when no `selector` argument is explicitly provided.

```{r global_option}
# Check the current default (usually empty)
getOption("IssueTrackeR.selector")

# Set a default selector
options(IssueTrackeR.selector = sel1)

# Now, get_issues() will use sel1 by default
# Note: This requires a working environment/token to actually run get_issues()

# Reset the option
options(IssueTrackeR.selector = init_selector())
```
